### 2015-02-20 fundamentals/impl.tex
for brevity
nonsense sentence

Nuclear engineering software quality is often governed by \gls{NQA1}, an
\gls{ASME} specification
whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}.
Although \gls{NQA1} is primarily
used for designing reactors, it is general enough to apply to
\Cyclus. \Cyclus has adopted an \emph{agile} development process
\cite{larman_agile_2004},
interpreting \gls{NQA1} in a manner similar to the process adopted by the
\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or the
PyNE toolkit \cite{biondo_quality_2014}.

Quality assurance is an on-going process throughout the entire life of the software. As a simulator where most modeling decisions are made
by third party archetype developers or users, the most important feature of
\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond
the scope of the kernel.

>>>>

Nuclear engineering software quality is often governed by \gls{NQA1}, an
\gls{ASME} specification
whose latest revision appeared in 2009 \cite{asme_nqa-1a-2009_2009}.
\Cyclus has adopted an \emph{agile} development process
\cite{larman_agile_2004},
interpreting \gls{NQA1} in a manner similar to the process adopted by the
\gls{DOE} within \gls{NEAMS} \cite{neams_nuclear_2013} or by the PyNE toolkit
\cite{biondo_quality_2014}.

Quality assurance is an on-going process throughout the entire life of the
software. Since \Cyclus modeling decisions are made
by third party archetype developers or users, the most important feature of
\gls{QA} is verification. Validation may be impossible and \gls{UQ} is beyond
the scope of the kernel.
